---
title: "Editing Excels with R"
author: "Edna Grewers"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Full Workflow}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignette is an addition to the [Full Workflow Vignette](./vignettes/full_workflow.Rmd). You can edit the created Excel files manually, or with R/RStudio. If you want to edit them via RStudio, here are some examples on how to do that.

For illustrative purposes we use a small example data set which comes alongside the package and contains different types of variables (e.g., numeric, categorical, pooled variables, scales). We import the data set using the `eatGADS` package, which is automatically installed when `eatCodebook` is installed.

```{r eatcodebook setup}
library(eatCodebook)
file <- system.file("extdata", "example2_clean.sav", package = "eatCodebook")
dat <- eatGADS::import_spss(file)
```


#### Setup

When editing all the created files in R, the script can get very long, so I recommend to use several .R documents to maintain an overview. 

First set up a new private repository in the [`iqb-research` project](https://github.com/orgs/iqb-research/repositories) and use the template `SHB_Erstellung_Vorlage`. You now have all the .R templates that you need, but you have to create your issues yourself.


```{r}


```








