---
title: "Full Workflow"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Full Workflow}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignettes describes the full workflow of creating a codebook via the `eatCodebook` package. For illustrative purposes we use a small example data set which comes alongside the package and contains different types of variables (e.g., numeric, categorical, pooled variables, scales). We import the data set using the `eatGADS` package, which is automatically installed when `eatCodebook` is installed.

```{r setup}
library(eatCodebook)
file <- system.file("extdata", "example1_clean.sav", package = "eatCodebook")
dat <- eatGADS::import_spss(file)
```

## Descriptive Statistics
On of the key elements of a codebook are descriptive statistics shortly describing each variable in the data set. What kind of descriptive statistics is reported for each variable depends on the type of the variable. The function `createInputForDescriptives()` creates a template to provide the information that is needed to calculate the descriptive statistics for an `GADSdat` object.

```{r createInputForDescriptives}
inputForDescriptives <- createInputForDescriptives(GADSdat = dat)
head(inputForDescriptives)
```

The template should be exported to `.xlsx`, modified and reimported to `R`.

```{r export varinfo, eval=FALSE}
writeExcel(inputForDescriptives, "file_path/inputForDescriptives.xlsx")
inputForDescriptives_edited <- getInputForDescriptives("file_path/inputForDescriptives.xlsx")
```

```{r edit varinfo, echo=FALSE}
inputForDescriptives_edited <- inputForDescriptives
```


This input is then used to calculate descriptive statistics via `calculateDescriptives()`.

```{r calculate descr}
# just show function calls
showFunctions <- calculateDescriptives(GADSdat = dat, inputForDescriptives = inputForDescriptives_edited, showCallOnly = TRUE)
showFunctions <- data.frame(varName = names(showFunctions), functionName = as.vector(showFunctions), stringsAsFactors = FALSE)
showFunctions

# acutally calculate descriptives
descStatistics <- calculateDescriptives(GADSdat = dat, inputForDescriptives = inputForDescriptives_edited, showCallOnly = FALSE)
descStatistics[[5]]
```


## Value and Missing Labels
Another imported part of a codebook is documentation of the value labels of valid and missing values. A respective overview is created via `createMissings()`.

```{r create missings}
missings <- createMissings(dat, inputForDescriptives = inputForDescriptives_edited)
head(missings)
```

In this case, the resulting object `missings` has to be written to `xlsx` and imported via `getMissings()`. Note that alle the `getXXX` functions perform important cleaning and preparation steps, therefore the exporting to `xlsx` is obligatory.

```{r write missings, eval = FALSE}
writeExcel(miss, "example_miss.xlsx", row.names = FALSE)
miss_final <- getMissings("example_miss.xlsx")
```

```{r load missings, eval = TRUE, echo = FALSE}
miss_file <- system.file("extdata", "example_miss.xlsx", package = "eatCodebook")
miss_final <- getMissings(miss_file)
head(miss_final)
```


## Variable Information
A key element of the `eatCodebook` package is that various forms of variable information can be supplied.

```{r create varInfo}
varInfo <- createVarInfo(dat, inputForDescriptives = inputForDescriptives_edited)
head(varInfo)
```

```{r write varInfo, eval = FALSE}
writeExcel(miss, "example_varInfo.xlsx", row.names = FALSE)
varInfo_final <- getVarInfo("example_varInfo.xlsx")
varInfo_final2 <- inferLayout(varInfo_final, GADSdat = dat, inputForDescriptives = inputForDescriptives_edited)
```

```{r load varInfo, eval = TRUE, echo = FALSE}
varInfo_file <- system.file("extdata", "example_varInfo.xlsx", package = "eatCodebook")
varInfo_final <- getVarInfo(varInfo_file)
varInfo_final2 <- inferLayout(varInfo_final, GADSdat = dat, inputForDescriptives = inputForDescriptives_edited)
head(varInfo_final)
```

## Structure
A key element of the `eatCodebook` package is that various forms of variable information can be supplied.

```{r create struc}
struc <- createStructure(varInfo_final)
head(struc)
```

```{r write struc, eval = FALSE}
writeExcel(struc, "example_struc.xlsx", row.names = FALSE)
struc_final <- getStructure("example_struc.xlsx")
```

```{r load struc, eval = TRUE, echo = FALSE}
struc_file <- system.file("extdata", "example_struc.xlsx", package = "eatCodebook")
struc_final <- getStructure(struc_file)
head(struc_final)
```

## Scale Information
A key element of the `eatCodebook` package is that various forms of variable information can be supplied.

```{r create scaleInfo}
scaleInfo <- createScaleInfo(inputForDescriptives_edited)
head(scaleInfo)
```

```{r write scaleInfo, eval = FALSE}
writeExcel(scaleInfo, "example_scaleInfo.xlsx", row.names = FALSE)
scaleInfo_final <- getScaleInfo("example_scaleInfo.xlsx")
# workaround, should be done automatically, but currently problem with non list inputs for createScaleInfo
scaleInfo_final$Quelle <- "dat"
```

```{r load scaleInfo, eval = TRUE, echo = FALSE}
scaleInfo_file <- system.file("extdata", "example_scaleInfo.xlsx", package = "eatCodebook")
scaleInfo_final <- getScaleInfo(scaleInfo_file)
# workaround, should be done automatically, but currently problem with non list inputs for createScaleInfo
scaleInfo_final$Quelle <- "dat"
head(scaleInfo_final)
```

## Register
Optionally, a register can be created. Thereby, keywords can be connected with certain variables.

```{r create register}
register <- createRegister(inputForDescriptives_edited, keywordList = c("kw1", "kw2"))
head(register)
```

```{r write register, eval = FALSE}
writeExcel(register, "example_register.xlsx", row.names = FALSE)
register_final <- getRegister("example_register.xlsx")
```

```{r load register, eval = TRUE, echo = FALSE}
register_file <- system.file("extdata", "example_register.xlsx", package = "eatCodebook")
register_final <- getRegister(register_file)
head(register_final)
```

## Literature Information
The literature information contains the sources which should be cited within the codebook. It builds on the references mentioned in the variable information.

```{r create litInfo}
litInfo <- createLitInfo(varInfo_final)
head(litInfo)
```

```{r write litInfo, eval = FALSE}
writeExcel(register, "example_litInfo.xlsx", row.names = FALSE)
litInfo_final <- getLitInfo("example_litInfo.xlsx")
```

```{r load litInfo, eval = TRUE, echo = FALSE}
litInfo_file <- system.file("extdata", "example_litInfo.xlsx", package = "eatCodebook")
litInfo_final <- getLitInfo(litInfo_file)
head(litInfo_final)
```


## Abbreviation List
An abbreviation list can be added which explains abbreviations or statistical symbols used throughout the codebook.

```{r create abbrList}
abbrList <- createAbbrList()
abbrList
```

```{r write abbrList, eval = FALSE}
writeExcel(abbrList, "example_abbrList.xlsx", row.names = FALSE)
abbrList_final <- makeAbbrList("example_abbrList.xlsx")
```

```{r load abbrList, eval = TRUE, echo = FALSE}
abbrList_file <- system.file("extdata", "example_abbrList.xlsx", package = "eatCodebook")
abbrList_final <- makeAbbrList(abbrList_file)
```

## Cover Page
A cover page can be added to the codebook.

```{r create cover}
cover <- makeCover(logoFile = NULL,
                   maintitle = "Study of Achievement",
                   subtitle = "Codebook of Study of Achievement",
                   authors = "Some Person",
                   addAuthors = "With the help of some other persons",
                   schriftenreihe = "Book 9 of Studies of Achievement",
                   bibinfo = "test")
```

## Meta data
Meta data can be added to the codebook.

```{r create meta data}
meta <- createMetadata()
meta[1, "Title"] <- "Codebook Test"
meta[1, "Author"] <- "Anna Muster"
meta[1, "Keywords"] <- "lsa, education"
meta[1, "Subject"] <- "test"
```

```{r write meta data, eval = FALSE}
writeExcel(abbrList, "example_meta.xlsx", row.names = FALSE)
meta_final <- makeMetadata("example_meta.xlsx")
```

```{r load meta data, eval = TRUE, echo = FALSE}
meta_file <- system.file("extdata", "example_meta.xlsx", package = "eatCodebook")
meta_final <- makeMetadata(meta_file)
```

## Further make steps
Further make steps are required.

```{r make steps}
cover <- makeCover(maintitle = "Study of Achievement", subtitle = "Codebook of Study of Achievement",
                   authors = "Some Person", addAuthors = "With the help of some other persons",
                   schriftenreihe = "Book 9 of Studies of Achievement", bibinfo = "test")

lit <- makeLit(litInfo_final)

hint <- makeBGM(varInfo_final)
```

## Chapters
Create the chapter structure.

```{r chapters}
chapters <- createChapters(varInfo_final2)
chapters[, 2] <- "Datensatz"
```


## Codebook
Now we create the actual codebook script via calling the `codebook()` function. 

```{r codebook, message=TRUE}
descStatistics2 <- descStatistics
descStatistics2$skala1[[2]] <- as.data.frame(descStatistics2$skala1[[2]])


latex_skript <- codebook(varInfo = varInfo_final2, missings = miss_final, struc = struc_final,
                         scaleInfo = scaleInfo_final, register = register_final, 
                         dat = eatGADS::extractData(dat), Kennwertedatensatz = descStatistics2, 
                         chapters = chapters, deckblatt = cover, intro = "", literatur = lit, 
                         abkuerzverz = abbrList_final, hintmod = hint, lastpage = "")
```

