---
title: "Minimal Example"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Minimal Example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignettes shows a minimal working example for creating a codebook via the `eatCodebook` package. For illustrative purposes we use the `R` built in data set `iris`. We import the data set using the `eatGADS` package, which is automatically installed when `eatCodebook` is installed. We also run the `checkFormat()` function from the `eatGADS` package which adds `SPSS` format information to the meta data of the data set.

```{r setup}
library(eatCodebook)
dat <- eatGADS::import_DF(iris)
dat <- eatGADS::checkFormat(dat)
```

## Descriptive Statistics
One of the key elements of a codebook are descriptive statistics shortly describing each variable in the data set. What kind of descriptive statistics is reported for each variable depends on the type of the variable. The function `createInputForDescriptives()` creates a template to provide the information that is needed to calculate the descriptive statistics for an `GADSdat` object.

```{r createInputForDescriptives}
inputForDescriptives <- createInputForDescriptives(GADSdat = dat)
head(inputForDescriptives)
```

The template should be exported to `.xlsx`, modified and reimported to `R`.

```{r export varinfo, eval=FALSE}
writeExcel(inputForDescriptives, "inputForDescriptives.xlsx")
inputForDescriptives_edited <- getInputForDescriptives("inputForDescriptives.xlsx")
```

```{r edit varinfo, echo=FALSE}
inputForDescriptives_edited <- inputForDescriptives
```


This input is then used to calculate descriptive statistics via `calculateDescriptives()`.

```{r calculate descr}
# calculate descriptives
descStatistics <- calculateDescriptives(GADSdat = dat, 
                                        inputForDescriptives = inputForDescriptives_edited)
descStatistics[[3]]
```


## Value and Missing Labels
Another important part of a codebook is the documentation of the value labels of valid and missing values. A respective overview is created via `createMissings()`.

```{r create missings}
missings <- createMissings(dat, inputForDescriptives = inputForDescriptives_edited)
head(missings)
```

In this case, the resulting object `missings` has to be written to `xlsx` and imported via `getMissings()`. Note that all the `getXXX` functions perform important cleaning and preparation steps, therefore the exporting to `xlsx` is obligatory.

```{r write missings, eval = FALSE}
writeExcel(missings, "example_miss.xlsx", row.names = FALSE)
miss_final <- getMissings("example_miss.xlsx")
```

```{r load missings, eval = TRUE, echo = FALSE}
miss_file <- system.file("extdata", "example_iris_miss.xlsx", package = "eatCodebook")
miss_final <- getMissings(miss_file)
head(miss_final)
```


## Variable Information
A key element of the `eatCodebook` package is that various forms of variable information can be supplied.

```{r create varInfo}
varInfo <- createVarInfo(dat, inputForDescriptives = inputForDescriptives_edited)
head(varInfo)
```

```{r write varInfo, eval = FALSE}
writeExcel(varInfo, "example_varInfo.xlsx", row.names = FALSE)
varInfo_final <- getVarInfo("example_varInfo.xlsx")
varInfo_final2 <- inferLayout(varInfo_final, GADSdat = dat, 
                              inputForDescriptives = inputForDescriptives_edited)
```

```{r load varInfo, eval = TRUE, echo = FALSE}
varInfo_file <- system.file("extdata", "example_iris_varInfo.xlsx", package = "eatCodebook")
varInfo_final <- getVarInfo(varInfo_file)
varInfo_final2 <- inferLayout(varInfo_final, GADSdat = dat, inputForDescriptives = inputForDescriptives_edited)
head(varInfo_final)
```

## Structure
A key element of the `eatCodebook` package is that various forms of variable information can be supplied.

```{r create struc}
struc <- createStructure(varInfo_final)
head(struc)
```

```{r write struc, eval = FALSE}
writeExcel(struc, "example_struc.xlsx", row.names = FALSE)
struc_final <- getStructure("example_struc.xlsx")
```

```{r load struc, eval = TRUE, echo = FALSE}
struc_file <- system.file("extdata", "example_iris_struc.xlsx", package = "eatCodebook")
struc_final <- getStructure(struc_file)
head(struc_final)
```

## Scale Information
A key element of the `eatCodebook` package is that various forms of variable information can be supplied.

```{r create scaleInfo}
scaleInfo <- createScaleInfo(inputForDescriptives_edited)
head(scaleInfo)
```

```{r write scaleInfo, eval = FALSE}
writeExcel(scaleInfo, "example_scaleInfo.xlsx", row.names = FALSE)
scaleInfo_final <- getScaleInfo("example_scaleInfo.xlsx")
```

```{r load scaleInfo, eval = TRUE, echo = FALSE}
scaleInfo_file <- system.file("extdata", "example_iris_scaleInfo.xlsx", package = "eatCodebook")
scaleInfo_final <- getScaleInfo(scaleInfo_file)
head(scaleInfo_final)
```


## Meta data
Meta data can be added to the codebook.

```{r create meta data}
meta <- createMetadata()
meta[1, "Title"] <- "Codebook Test"
meta[1, "Author"] <- "Anna Muster"
meta[1, "Keywords"] <- "lsa, education"
meta[1, "Subject"] <- "test"
```

```{r write meta data, eval = FALSE}
writeExcel(meta, "example_meta.xlsx", row.names = FALSE)
meta_final <- makeMetadata("example_meta.xlsx")
```

```{r load meta data, eval = TRUE, echo = FALSE}
meta_file <- system.file("extdata", "example_iris_meta.xlsx", package = "eatCodebook")
meta_final <- makeMetadata(meta_file)
```

## Chapters
Create the chapter structure.

```{r chapters}
chapters <- createChapters(varInfo_final2)
chapters[1, 2] <- "Iris Datensatz"
```

## Codebok
Now we create the actual codebook script via calling the `codebook()` function.

```{r codebook}
latex_skript <- codebook(varInfo = varInfo_final2, missings = miss_final, struc = struc_final,
                         scaleInfo = scaleInfo_final, dat = eatGADS::extractData(dat),
                         Kennwertedatensatz = descStatistics, chapters = chapters)
```

## Save the Codebok
The resulting object and the meta data are then separately save to the hard drive. Both objects should be saved into the same folder.

```{r save codebook, eval = FALSE}
write.table(latex_skript , file = "minimal_example.tex" , fileEncoding="UTF-8" ,
            col.names=FALSE , row.names=FALSE , quote = FALSE )
write.table(meta_final , file = "minimal_example_meta.xmpdata", fileEncoding="UTF-8" ,
            col.names=FALSE , row.names=FALSE , quote = FALSE )
```

## Compilation
The `LaTeX` script for the codebook has now been saved to the hard drive. This file should now be opened via a `Tex`-Editor and simply compiled. Sometimes multiple consecutive compilation steps are required for a clean output. Alternatively, the document can be compiled from within `R`, for example via `tools::texi2pdf()`.
